Modeling trend in temperature volatility using generalized LASSO

### 2018-05-17 nips-2018/paper.tex
updates on paper

\subsection{Data analysis}

@@

???

To remedy this, we add the following long horizon penalty
to \eqref{eq:l1tf_var}:

\attn{From here down needs to be cut down and corrected with the right numbers.}

@@

We used the following rule to determine when to stop the optimization:
the optimization was stopped if the value of the loss did not improve
by at least 0.1\% in 1000 trials. As we can see, the algorithm
converged in about 2000 iterations. This took about 11 minutes. Our
experiments showed that the convergence speed depends on the value of
$\lambda_t$ and $\lambda_s$. Also, if we use the solution obtained for
smaller values of these parameters as the initial value for the larger
values (\textit{warm start}), the converges speed improves.

@@

We computed the optimal solution for all the combinations of the
following sets of values: $\lambda_t \in \{0,2,4,8,10,15,200,1000\} \, \, ,
\lambda_s \in \{0,.1,.5,2,5,10\}$. The best combination based on a held
out set was $\lambda_t=4$ and $\lambda_s=2$. All the analyses in the
next section are performed on the solution for these values.

@@

The red curve in the left panel of \autoref{fig:bloom_estimatedSD}
shows the estimated SD (which is $\exp(h_t/2)$) of the residuals of
the time-series of Bloomington. To reduce the number of time-steps in
this figure and in the remainder of the paper we work on the weekly
averaged of the data.

The curve of the estimated SD captures the periodic variations in the
SD of the signal. Just by looking at this curve, it is hard to say if
the SD is decreasing or increasing. Therefore, we compute the average
of the estimated SD for each year. The estimated SD together with this
annual average is shown in the middle panel of
\autoref{fig:bloom_estimatedSD}. As it can be seen, the annual trend
is not smooth. This is because in the optimization problem
\eqref{eq:l1tf_var}, the smoothness of the annual trend is not
encouraged. To remedy this, we proposed a method to encourage the smoothness of the annual average trend. The estimated SDs using this method is shown in the right panel of \autoref{fig:bloom_estimatedSD}. The annual average of the estimated SDs shows a linear trend with a positive slope.

>>>>

\subsection{Data analysis}
\label{sec:data}

@@

In Appendix D, we investigate some properties of the time-series of different locations on earth. We also explain how each time-series is detrended using $\ell_1$-trend filtering method explained in \autoref{sec:ell_1-trend-filt}. \autoref{fig:bloom_estimatedSD} shows a time-series after detrending using this method. The variance of this time-series have a cyclic behavior. The cycles are not regular and their amplitude and frequency change. In addition, the time-series of other locations show different patterns. These observations motivate the need to develop a non-parametric framework for the problem at hand. In this figure, the estimate SD obtained from the method of \autoref{sec:l1tf_var} is also shown. Sine the estimated SD captures the periodic behavior of volatility, it is hard to see the trend in volatility based on these estimated values. Therefore, we compute the annual average of these estimates. However, as this figure shows, the annual trend is not smooth. This is because in the optimization problem \eqref{eq:l1tf_var}, the smoothness of the annual trend is not encouraged. Therefore, in Appendix D we propose a simple method to encourage the smoothness of the annual average trend. The estimated SDs using this method is shown in the right panel of \autoref{fig:bloom_estimatedSD}. The annual average of the estimated SDs shows a linear trend with a positive slope.

@@

We used the following rule to determine when to stop the optimization: the optimization was stopped if the value of the loss did not improve by at least 0.1\% in 1000 trials. Our experiments showed that the convergence speed depends on the value of $\lambda_t$ and $\lambda_s$. Also, if we use the solution obtained for smaller values of these parameters as the initial value for the larger values (\textit{warm start}), the converges speed improves.

@@

We computed the optimal solution for all the combinations of the
following sets of values: $\lambda_t \in \{0,2,4,8,10,15,200,1000\} \, \, ,
\lambda_s \in \{0,.1,.5,2,5,10\}$. The best combination was $\lambda_t=4$ and $\lambda_s=2$. All the analyses in the next section are performed on the solution for these values.

@@

The red curve in the left panel of \autoref{fig:bloom_estimatedSD}
shows the estimated SD (which is $\exp(h_t/2)$) of the residuals of
the time-series of Bloomington obtained from out proposed model. To reduce the number of time-steps we work on the weekly averaged of the data. The curve of the estimated SD captures the periodic variations in the
SD of the signal. Just by looking at this curve, it is hard to say if
the SD is decreasing or increasing. Therefore, we compute the average
of the estimated SD for each year. The estimated SD together with this
annual average is shown in the middle panel of
\autoref{fig:bloom_estimatedSD}. As it can be seen, the annual trend
is not smooth. This is because in the optimization problem
\eqref{eq:l1tf_var}, the smoothness of the annual trend is not
encouraged. To remedy this, we add the following long horizon penalty to \eqref{eq:l1tf_var}:
